Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-10 manuscript/cpcrw_manuscript.Rmd
Added CO2:CH4 ratio computation and ms text

* CO2:CH4 ratios
* Statistical tests of WC and temperature on cumulative fluxes

>>>>

* CO2:CH4 ratios

```{r, echo=FALSE}
minmag <- min(gas_ratio$CO2CH4_ratio) %>% log10 %>% floor %>%
  c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine")[.]
minratio <- min(gas_ratio$CO2CH4_ratio / 1e6)  %>% formatC(digits = 1, format = 'f')
mintrt <- gas_ratio$Treatment[which.min(gas_ratio$CO2CH4_ratio)]
mintemp <- gas_ratio$Temperature[which.min(gas_ratio$CO2CH4_ratio)]
maxratio <- max(gas_ratio$CO2CH4_ratio / 1e6) %>% formatC(digits = 1, format = 'f')
maxtrt <- gas_ratio$Treatment[which.max(gas_ratio$CO2CH4_ratio)]
maxtemp <- gas_ratio$Temperature[which.max(gas_ratio$CO2CH4_ratio)]
```

The production of C from CO~2~ was over `r minmag` order of magnitudes higher than that from CH~4~, with CO~2~:CH~4~ ratios ranging from `r minratio` million in the `r mintemp` °C `r maxtrt` treatment, to `r maxratio` million in the `r maxtemp` °C `r maxtrt` treatment.

* Statistical tests of WC and temperature on cumulative fluxes
